\documentclass[10pt,a4paper,roman]{moderncv}\moderncvtheme[blue]{classic}\usepackage[utf8]{inputenc}\usepackage[scale=0.86]{geometry}\nopagenumbers{}\setlength{\hintscolumnwidth}{2.65cm}\title{Cloud Engineer/Full Stack Developer}\firstname{Badreddine}\familyname{Gharbi} \address{Martyrs street}{3013 Sfax Tunisia}\mobile{(+216) 54 117 244}\email{gh.badreddine@hotmail.com}\begin{document}\maketitle\vspace{-1.2cm}\section{Education}\vspace{-0.1cm}\cventry{2019 (ongoing)}{Cloud Engineer }{}{\newline{} Google/Andela Africa Certifications Scholarships 2019}{}{}\cventry{2019}{Full Stack developer }{}{\newline{} Gomycode Tunisia}{}{}\cventry{2018}{The Web Developer Bootcamp }{}{\newline{} Udemy }{}{}\cventry{2016 -- 2017}{Postgraduate Degree in Petroleum Engineering }{}{\newline{} Oil and Gas Institute of Monastir (OGIM)}{}{}\cventry{2013 -- 2016}{Hydraulics and Rural Development Engineering }{}{\newline{} National Institute of Agronomy - Tunis}{}{}\cventry{2010 -- 2013}{Biology and Geology Preparation (BG)}{}{\newline{} Sfax Preparatory Engineering Institute }{}{}\vspace{-0.3cm}\section{Work Experience}\vspace{-0.1cm}\cventry{Sep 2019 -- 2019(ongoing)}{Andela cloud mentor volunteer (Part Time)}{}{\newline{}- Advise and help to accomplish Google cloud quicklabs(Docker, Kubernetes, Networking ...) .\newline{}- Answer students questions }{}{}{}\cventry{June 2019 -- 2019(ongoing)}{Fullstack Personal project (Ecommerce web App)}{}{\newline{}- Firebase Authentication.\newline{}- Schema Design and Data Modeling in MongoDB.  \newline{}- React Dynamic web pages}{}{}{}\cventry{February 2019 -- April 2019}{Fullstack Personal project (CV Builder web App)}{}{\newline{}- Node.js - Expressjs routing.\newline{}- Authentication with Passport.js.\newline{}- Schema Design and Data Modeling in MongoDB.  \newline{}- Dynamic web pages}{}{}{}\cventry{December 2017 -- February 2019}{Hydraulic Engineer (ATIA association)}{}{\newline{}- Designing and sizing water irrigation network. \newline{}- Agriculture project planning.\newline{}- Work supervision.  \newline{}- Event management}{}{}{}\cventry{January 2016 -- June 2016}{Engineer trainee (Real Estate Housing Agency)}{}{\newline{}- Hydrological study of the area.\newline{}- Water supply study.\newline{}- Waste water network study. }{}{}{}\cventry{August 2015}{Engineer Intern (National Water Distribution Utility)}{}{\newline{}- Creating a geographic information system of water network.\newline{}- Water simulation using EPANET. \newline{}- Optimization of water distribution network design}{}{}{}\vspace{-0.4cm}\section{Languages }\vspace{-0.1cm}\cvcomputer{Arabic}{Mother tongue}{French}{Fluent (TCF:B2)}\cvcomputer{English}{Fluent (TOEIC: 910)}{Italian }{Basic}\vspace{-0.4cm}\section{Software Skills}\vspace{-0.1cm}\cvcomputer{Cloud}{Docker, Kubernetes, Application deployment}{Hydraulic software}{Epanet, ArcGis, Covadis}\cvcomputer{Programming languages}{Python, HTML, CSS, Javascript, React, Mongodb, NodeJs, Git.}{Office 365}{Microsoft Office, Open Office} \vspace{-0.4cm}    \section{Hobbies/Interests}\vspace{-0.1cm}\cvline{}{Cooking, Sport, Musique.}\end{document}



